### 2015-02-23 fundamentals/impl.tex

When decay is invoked, A material checks to see if it contains any nuclides with
decay constants that are significant with respect to the time change since the
last decay operation.  If none of the decay constants are significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time change will be larger.

>>>>

When decay is invoked, a material checks to see if it contains any nuclides with
decay constants that are significant with respect to the time change since the
last decay operation.  If none of the decay constants are significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time change will be larger.
